A novel route to crystallization via viscoelastic phase separation

### 2015-10-20 crystal-gel/science/coverl_letter.tex

Understanding the process of crystal growth in mixed-phase systems is of fundamental importance,
and has several technological applications. As an example, understanding
water crystallization in clouds is recognized as one of the main challenges in the
modeling of Earth's radiation budget and climate. \textcolor{red}{Moreover, our study addresses the formation of crystal networks,
which are observed in many systems, including magma, biominerals and foods, where the origin
and formation of the networks still lacks fundamental understanding.}
The difficulties arise both from our poor understanding of small-scale microphysical effects,
and to the difficulty of experimental investigations. In our colloidal system, both
difficulties are overcome due to the colloid's accessible length and time scales.

>>>>

Understanding the process of crystal growth in mixed-phase systems is of fundamental importance,
and has several technological applications. As an example, understanding
water crystallization in clouds is recognized as one of the main challenges in the
modeling of Earth's radiation budget and climate. Moreover, our study addresses the formation of crystal networks,
which are observed in many systems, including magma, biominerals and foods, where the origin
and formation of the networks still lacks fundamental understanding. 
The difficulties arise both from our poor understanding of small-scale microphysical effects,
and to the difficulty of experimental investigations. In our colloidal system, both
difficulties are overcome due to the colloid's accessible length and time scales.

### 2015-10-20 crystal-gel/science/crystal_gel_letter3.tex

\maketitle
\vspace{-1.5cm}
\begin{sciabstract}

With confocal microscopy measurements we find a novel crystallization pathway of a colloid-polymer mixture undergoing viscoelastic
gas-liquid phase separation. We show that crystallization leads to a network structure different from the original phase separation pattern.
Crystals nucleate inside the liquid network, but grow past it by direct condensation of the gas phase on their surface,
driving evaporation of nearby liquid. This process represents the colloidal analogue of the Bergeron process, i.e.,
ice crystals formation in mixed phase clouds and is at the origin of rain. Our finding gives us full experimental
access to the kinetic pathway of this phenomenon important for climate science. We argue that similar states can form as the
result of the gas-liquid phase separation of crystallizable components, such as monoatomic and molecular systems,
if dynamics of the liquid phase is slow enough to induce viscoelastic phase separation, but fast enough to prevent immediate 
vitrification.
\end{sciabstract}

>>>>

\maketitle
\vspace{-1.5cm}
\begin{sciabstract}
With confocal microscopy measurements we find a novel crystallization pathway of a colloid-polymer mixture undergoing viscoelastic gas-liquid phase separation. We show that crystallization leads to a network structure different from the original phase separation pattern. Crystals nucleate inside the liquid network, but grow past it by direct condensation of the gas phase on their surface, driving evaporation of nearby liquid. This process represents the colloidal analogue of the Bergeron process, i.e., ice crystals formation in mixed phase clouds and is at the origin of rain. Our finding gives us full experimental access to the kinetic pathway of this phenomenon important for climate science. We argue that similar states can form as the result of the gas-liquid phase separation of crystallizable components, such as monoatomic and molecular systems, if dynamics of the liquid phase is slow enough to induce viscoelastic phase separation, but fast enough to prevent immediate vitrification.
\end{sciabstract}
